Speed and strength of epidemic intervention

### 2019-07-09 doc/speedstrength.tex
minor tweaks

\subsection{Control strategies}

We assume that the effectiveness of intervention strategies $L(\tau)$ varies over the course of infection.

>>>>

\subsection{Speed and strength of epidemic intervention}

We assume that the intervention strategies $L(\tau)$ vary over the course 
of infection such that the effective kernel can be written as 
$\hat K(\tau) = K(\tau)/L(\tau)$. For example, constant
